\resumeSubHeadingListStart
  \resumeProjectHeading
       {\titleItem{{Internship Full-stack Developer [Company Career Web]}} $|$ \emph{PT. Satkomindo Mediyasa}}{February 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Developed frontend and backend for the dashboard, CV log feature, and authentication system using AdonisJS, React Vite, Ant Design, Tailwind CSS, and Zustand.}
    \resumeItem{Created role management for user/admin roles with CRUD operations, automated PDF CV generation, and integrated a rich text editor for job descriptions. Managed dynamic data updates and ensured seamless admin review tracking.}
    \resumeItem{Overcame cache issues and file validation problems, navigated complex Ant Design configurations, and adapted to documentation challenges, gaining valuable experience in backend operations, RESTful APIs, and Docker.}
  \resumeItemListEnd
\vspace{2pt}
\resumeProjectHeading
  {\titleItem{Electro-Programming Division Leader} $|$ \emph{Barunastra ITS}}{April 2022 -- Present}
  \resumeItemListStart
    \resumeItem{Assisted with ASV testing and object dataset processing in the International Roboboat Competition 2022, contributing to the Grand Champion title.}
    \resumeItem{Main programmer for ASV in the International Roboboat Competition 2023 and KKCTBN 2023, developed program using ROS1 and YOLOv4 Tiny 3L, achieving the Grand Champion title.}
    \resumeItem{Led Electro-Programming Division for IRC and KKCTBN 2024, overseeing ASV development.}
    \resumeItem{Led ATSV sub-division and programming team in KKCTBN and International Roboboat Competition 2024, achieving 1st place in KKCTBN and 3rd place in the International Roboboat Competition, mainly using ROS2 Humble and YOLOv8.}
  \resumeItemListEnd
\vspace{2pt}

  \resumeProjectHeading
       {\titleItem{{Navigation Programmer ITS Ocean Survey USV}} $|$ \emph{ITS - PT. Robomarine Indonesia}}{July 2023 -- December 2023}
  \resumeItemListStart
    \resumeItem{Developed algorithms for Autonomous Surface Vehicles (ASVs) to follow mapping routes efficiently.}
    \resumeItem{Implemented obstacle avoidance using camera (YOLO) and LiDAR to ensure safe survey navigation. }
    \resumeItem{Created a control interface for the USV using Next.js, roslib.js, and Tailwind CSS, enhancing usability.}
    \resumeItem{Integrated ITS software with PT Robomarine's mechanical systems to provide a comprehensive USV solution.}
    \resumeItemListEnd
\vspace{2pt}

   \resumeProjectHeading
       {\titleItem{{Frontend Developer}} $|$ \emph{MAGE 9 ITS}}{January 2023 --  February 2024}
  \resumeItemListStart    
    \resumeItem{Developed the frontend for the event's website using Next.js, Tailwind CSS, and Firebase.}
    \resumeItem{Implemented user authentication with secure login and registration, forgot password functionality, email verification, and multi-platform login using Firebase Authentication \href{https://github.com/agus-darmawan/mage9-frontend}{[github]}.} 
  \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{4pt}
